### 2020-12-11 ch/1-introduction.tex
Write first two paragraphs

\chapter{Introduction}\label{ch:introduction}
\section{Problem statement}
In order for the use of \ac{ML} systems to be acceptable in wider society,
they have to be trustworthy.
This means that

>>>>

\chapter{Introduction}\label{ch:introduction}
\section{Problem statement}
In order for \ac{ML} systems to be used more widely,
they have to become more trustworthy.
The susceptibility of \ac{ANNs} to adversarial attacks has been well documented, but there are other problems as well.
This includes their opaqueness and their general tendency to take shortcuts;
leading to situations where \ac{ANNs} do not do `what we meant', but just what they were explicitly told to do.

This problem becomes especially severe when the training data is biased in some way,
which, by default, makes the \ac{ML} system copy the bias, or even exacerbate it.
The topic of this thesis is how to deal with biased data;
what types of bias exist and how to correct it if possible.

\section{Motivation and aims}
